% !TeX spellcheck = en_US

\section{Loek}
\label{sec:loek}

\begin{goal}{Improve quality management skills}
	\Description{I'd like to improve the way I act as a quality manager in a project. I want to know I can write a complete quality plan and can be assertive in maintaining the project's quality through defined standards and processes and reviews}
	\Measurement{Assessing whether the quality management document is complete in defining standards and helpful to the project by using a survey}
	\Measurement{Assessing if I can be a critical and helpful reviewer by using a survey}
	\Criteria{If the group thinks the quality management plan addresses all it's issues}
	\Criteria{If the group thinks the quality management processes defined are useful}
	\Criteria{If every project artifact is according to the quality standards}
	\Criteria{If the group finds that I correctly review and improve their documents and code}
\end{goal}

\begin{goal}{Improve versioning skills}
	\Description{Improve my skills in working with versioning and having a proper workflow and delivering useful commits}
	\Measurement{Having the group review all my commits and branches. Commits should be small and deliver a single feature and commit messages should be descriptive. The same with branch names when merging new features}
	\Criteria{If I have less negative code reviews on my commit content and names in the end than in the beginning}
	\Criteria{If I correctly use branches to merge new features and do not commit directly to the master branch in the end}
\end{goal}

\begin{goal}{Improve Scrum skills}
	\Description{I'd like to improve the way I work inside a Scrum environment. My problem is getting into the rhythm of correctly defining backlog items and developing a product bit by bit instead of the waterfall method of doing every thing a little bit.}
	\Measurement{Measuring group's satisfaction with our implementation of Scrum using a short survey}
	\Measurement{Measuring the progress and status of the project after each Sprint}
	\Criteria{If the group was happy with our implementation of Scrum according to a survey}
	\Criteria{If after each sprint only the selected backlog items for that sprint have been worked on}
	\Criteria{If after each sprint the product is in a working state and is of high quality as per the quality standards. The product should be demonstrable to the customer after every sprint. Not all backlog items have to be implemented. This is more important near the end of the project than in the beginning}
\end{goal}
