% !TeX spellcheck = en_US

\section{Tobias}
\label{sec:tobias}


\begin{goal}{Improve Git collaboration skills}
	\Description{My skills using the git collaboration features should be increased. This includes the use of branches, pull requests and tags. Furthermore Github provides some extra features on top of the git functionality.}
	\Measurement{Regular use of pull requests and branches and let them be reviewed by someone else.}
\end{goal}

\begin{goal}{Production of high quality documents}
	\Description{There are a lot of documents and code to produce during the module. These documents and code should be reviewed by at least one other group member. Furthermore the documents should be accord with our quality standard defined in the quality plan.}
	\Criteria{All documents produced has been reviewed by someone else.}
\end{goal}

\begin{goal}{Creation of a software architecture}
	\Description{Create a software architecture which meets the requirements, identified and agreed upon. The architecture can consists of multiply layers and multiple technologies to use.}
	\Measurement{Architecture meets the non-functional requirements as agreed on by the customer.}
	\Criteria{Architecture meets at least 85\% of the non-functional requirements.}
\end{goal}

\begin{goal}{Working with Scrum}
	\Description{Developing an application using the Scrum agile way of developing. By utilizing Scrum to develop the software our team will be more flexible to requirement changes and can deliver a high quality product at several instances during the development. This will help us to deliver a useful and tested application.}
	\Measurement{Definition of Product Backlog, Sprints and Sprint Backlogs will be assessed.}
	\Criteria{After each sprint the product is in a well-defined and deployable state. It is not needed that all user stories of a sprint has been implemented or that all planned sprints has been carried out successfully. The main focus is to deliver a functioning and tested product.}
\end{goal}