\newpage
\section{Development Plan}
\label{sec:development}

\subsection{Software management}
As group'ss Configuration Manager, level 3 of software management will be reached. The configuration manager will keep track of software and is responsible of deliverables. As individual programmer there also lies the responsibility to manage the software written.\\  
To properly fulfill my configuration manager I will pro-actively address other users of the group to fill in their created artifacts in the CI table and keep them updated. Evidence can be found in SCRUM meetings. I'm also responsible for the delivery of sprint products to the customer.  \\
As group member I will also make entries into the Configuration Item (CI) table of my created artifacts and keep them updated. \\


\subsection{Software advice}
The research described in 5.1 will enable me to give an advice to the group. This research is done on my own initiative and using the research I will give an advice to the group pro-actively. During the daily SCRUM meetings I will also give advice during SCRUM meetings on what's best to implement. My role as Software Architect will help me give advice related to the front-end back-end communication.

\subsection{Design}
My second role in the group is as software architect. What this means is that I am responsible for the front-end back-end communication. I will document, create, update and communicate this design.
I will be proactive on the designing part and innovative in finding solutions that fit with each sprint. The back-end architecture document will be proof of this process. Also other members using and implementing will be proof of reaching level 3 according to the HBO-I matrix.

\subsection{Software Implementation}
For Software Implementation I will learn a new framework and use it. I will communicate with interested parties within the group about the code I produced. I will document it and work SCRUM based. I will solve software problems front-end in an innovative way. The proof will be the code I produced, an example is using an in memory database to produce .

\subsection{Professional Behavior}
In the daily meetings I will report on my done work and discuss the best path for the group. I will try to motivate the group to work harder by surprising them using innovative means. An example would be giving motivational speeches. Other ways can be found during the daily group minutes.

\subsection{Research skills, for more information see 5.1}
I will choose a research topic that contributes to the project and will be used by the group. I will choose objective based criteria to make sure the research is valuable. Because we work in a group I will also take the skills and wishes of the group members into the research. The research will be proof of my Level 3. If the conclusion of my research is accepted by the group it shows Level 3 criteria as well. I will take godo care in finding good frameworks and proactive in analyzing the groups learning curve for the framework.
