\section{Development Plan}
\label{sec:development}
This section describes how I plan to reach the targeted skill levels and how i measure or prove that I reached them.

\subsection{Professional Behavior}
The skill Professional Behavior on level 3 will be reached by executing my role as project leader. The project leader is responsible for the contact with the customer and other external partners in a professional way. 
\newline
Furthermore a project leader creates a project plan during the project, with that and the written communication I want to improve my English writing skills by counting the errors in documents that I write. The progress will be monitored with the help of our group coach to ensure that the skill level is reached.

\subsection{Implement Software}
The skill Manage Software on level 3 will be reached by creating a project where I have to build a system in line with existing systems and on basis of designed architectures 
using existing frameworks. We decided to use the "Angular" framework for our front-end and I have to learn how to implement a software product using this framework. I will pay special attention to the so-called angular "components" in order to create our application according to the typical features of an angular application. I take the initaive to complete the researh of "Angular" with findings during the use of Angular.

\subsection{Advise Software}
The skill Advise Software on level 3 will be reached by creating a product where I give advice regarding the framework "Angular" we use for our front-end in relation to the software architecture in which cost and quality aspects, such as availability, performance, security and scalability are important key performance indicators. I will regulary practise review sessions to realise this goal.  I will focus my advice especially on structuring our application with "Components", a feature of  the Angular framework. Furthermore decisions regarding a software development process are part of it.   

\subsection{Research Skills}
To reach level 3 with the skill Research a research have to be made during the project. To see more information about that please look at Chapter \ref{sec:research}.