\section{Development}
The developments of my competences will be described here.

\textbf{Business Process Advise 3}:\\
During the SoFa project a research report needs to be done. As I have completed the Minor Research and Innovation during semester 6 I can advise the group members how to write a proper research document and change it whenever feedback arrives. This will show initiative into improving my project members research reports and advising them on how to write one.

\textbf{Software Analyse 2 to Software Analyse 3}:\\
During the SoFa project I will participate in building the Software Requirements Specification document according to customer requirements from Mr. V.d Ham  and I will participate in forming acceptance criteria for user stories each sprint as Scrum Master. This is innovative for me as I have never worked as Scrum Master and set up proper acceptance criteria for sprint backlogs. This will be done using cards to guess how difficult a certain sprint item will be. This progress will be demonstrable on the daily logs and our Trello project page.

\textbf{Software Design 2 to Software Design 3}:\\
During the SoFa project I will make the backend tests, namely both unit and integration tests that will have to cover the code 100\%. These tests will be white-box and black-box tests to ensure the code runs properly and will not break with any unexpected input. This is innovative for me as the tests will have to interact with an online REST API, and mocking the database layer using multiple frameworks, something which has not been taught here a is new to me. I will have to research ways to do this properly and construct new ways to test complicated infrastructure.

\textbf{Professional Behavior 3}:\\
As Scrum Master I will have to moderate every meeting and ensure a professional atmosphere is kept. By communicating with project members and the customer I will make sure that all meetings are smooth and go as planned. This will show initiative into working in a Scrum oriented way.