\section{Roles and Responsibilities}

\subsection{Stakeholders}
\begin{table}[h]
    \centering
    \begin{tabular}{l|l|l|l}
        \textbf{Role}               &   \textbf{Name}           &   \textbf{Interest}     &     \textbf{Influence}  \\ \hline \hline
        Customer                    &   Van den Ham, Richard    &   High                  &     High                \\ \hline
        Users of the Product        &   IT Teachers             &   High                  &     Medium              \\ \hline
        Users of the Product        &   Students                &   Medium                &     Low                 \\ \hline
        Coach                       &   Jacobs, Jan             &   High                  &     Medium              \\ \hline        
    \end{tabular}
    \caption{Stakeholders}
\end{table}

\subsection{Team}
    \subsubsection{Nils Nieuwenhuis: Project Manager}
    The project manager is responsible for the planning
    and will keep in touch with the customer due to the limited time. The project manager will write and
    keep the project management plan up to date. He will also keep a tight watch on the available
    resources. The project manager is responsible for the agenda of each meeting.
    
    \subsubsection{Loek Ehren}
    \textbf{Quality Manager:}
    The reviewing process of the project deliverables is managed by the quality manager. He has the responsibility to check 		that nothing leaves
    the team without testing and for that he writes a quality management plan and keeps it up to date. He also archives the 		reports produced
    in the test processes. 
    \newline
    \newline
    \textbf{Scrum Master:}
    The scrum master is not a traditional team lead or project manager but acts as a buffer between the team and any distracting influences. The scrum master helps to ensure the team follows the agreed processes in the Scrum framework, often facilitates key sessions, and encourages the team to improve.  

    \subsubsection{Sjoerd Brauer: Configuration Manager}
    The configuration manager has to document
    the use and / or modification of any hardware related configuration item as well as the use of the
    software and document related configuration items. Everything will be documented in the configuration management plan
    by the configuration manager.
   
    \subsubsection{Tobias Derksen: DevOps Engineer}
    A DevOps engineer is an information technology (IT) professional who works with software developers, 	system operators (SysOps) and other production IT staff to oversee code releases. The role calls for 	someone who has the necessary hard and soft skills that are required to overcome the traditional 			barriers between software development, testing and operations teams.  
