\section{Introduction}
\label{sec:intro}

This document defines the development of personal skills during the Software Factory (SoFa) module.
During this module some learning goals should be met which contributes to the final skills of the Informatics study.
~\\
Section \ref{sec:current} provides an overview over the current skill level (see table \ref{currentskills}) according to the HBO-I matrix as defined in \glqq HBO-I Domain Description Bachelor of ICT\grqq.

The next section deals with the target skill level (see table \ref{targetskills}) and how this level will be accomplished. The concrete improvements are marked in red.

The third section explains how the target skills will be reached in detail. It defines how the progress will be measured and when at which point the target will be reached.

As part of the learning goals, a topic has to researched. This research topic will be described in section \ref{sec:research}.

\subsection{Roles during the Project}

During the project, I have to fulfill some roles inside the team. These roles are described here:

\paragraph{DevOps Engineer} As a DevOps Engineer I have to create a test plan for the software artifacts, setup continuous integration services for the software components and - if supported by the customer - setup a continuous delivery or deployment pipeline, which automates the roll out of the release after each sprint.

\paragraph{Software Developer} As a Software Developer I have to implement certain software functions as defined in the product backlog. I will be part of a team of developer who work together to produce a useful, running and well tested product.

\subsection{Learning Goals}
\label{ssec:learning}
The learning goals of the module Software Factory (SoFa) as defined in the module description are:

\begin{itemize}
	\item[\textbf{LG1}] Show professional behavior in a project with a real customer (e.g. communication, collaboration, problem orientation and effectiveness, criteria-based decision making, systematic and well-structured process)
	\item[\textbf{LG2}] Fulfill a function relevant for a development project (e.g. project manager, scrum master, quality manager, configuration manager, software architect, software developer – other functions need to be approved the group’s coach)
	\item[\textbf{LG3}] Define a research topic relevant to the project, do the research, report on it and care foradequate application of the results in the project.
	\item[\textbf{LG4}] Deliver a relevant contribution to the project (next to his/her function and research topic) in three activities (of Manage, Analyse, Advice, Design and Realise) on any architectural layer (User Interaction, Business Processes, Infrastructure, Software, Hardware Interfacing)
	\item[\textbf{LG5}] Work together (communication, systematic and well-structured process).
	\item[\textbf{LG6}] Deliver results relevant to the customer and of adequate quality.
	
	\captionof{table}{Learning Goals according to the Module Description}
	\label{table:learninggoals}
\end{itemize}
