% !TeX spellcheck = en_US
\section{Research Topic}
\label{sec:research}

As research topic I will research on different approaches how to set up a continuous integration and continuous delivery infrastructure.

Therefore I need to research current industry standards as well as bleeding edge technology approaches for example infrastructure as a service or containerization. Continuous integration as a concept, exists for quite a while now. Continuous delivery is a rather new concept which reduces development cycles and simplifies the software roll-out process. The implementation of this concepts was rather complex and error-prone and often did deliver what was expected.

One of the most interesting upcoming technologies, containerization (i.e. Docker) allows now to implement the concepts in a very easy and reproducible  way. Setting up the whole development environment can now be automatically done by a container tool, which allows to test and deploy software wherever the container tool works, without being dependent on specific framework requirements. 

For our project I want to incorporate the concepts of continuous integration and deployment by researching about the newest concepts and approaches in using containerization and automation for software development. 
Therefore at first I will conduct a trend research about virtualization and containerization. After that I will look up the current industrial standards for software development. Industry companies are usually more conservative when it comes to new technologies, so they normally adopt the technology at a later point in the hype cycle. 
Finally I will have a look at upcoming developments and what can be possible in the future.

Prior to the research, I will define requirements which should be met by this infrastructure (see Section \ref{ai3}).
The results of the research will be composed into a report. Part of this report will be a proposal for a concrete infrastructure which meets the predefined requirements and can be implemented in our project (see Section \ref{ii3}).