% !TeX spellcheck = en_US
\documentclass[11pt]{meetingmins}

\input{../base}

\setdate{November 06, 2017}


\setpresent{
	\chair{L.~Ehren},
	S.~Brauer,
	\secretary{T.~Derksen}
}

\absent{N.~Nieuwenhuis \textit{(sick)}}
\customer

\begin{document}
\maketitle

\section{Agenda}
\begin{hiddenitems}
	\item Customer Remarks
	\item Questions to Customer
	\item Acceptance of User Story
	\item Next
\end{hiddenitems}

\section{Customer Remarks}
Hide fields which are empty, only if this will not break the layout.

Provide HVD with current database schema.

Change description in curriculum button: Show long description instead of short abbreviation.
Module Overview: Show real module name in small font.

Put project at the end of the row. Add flag to module whether project or not.

Additional Information field: Compose assessment information out of normalized database structure
-> Not relevant for accreditation

Introduction: Implement new line detection to show it properly.


\section{Questions to Customer}
What about peerweb authentication:
- Still in pipeline with HOM
- With docker host

\section{Acceptance of User Story}

The customer accepts the user story.


\section{Next}
Show qualifications after semester
-> Add link on semester name in module overview and navigate to new view

Filter on curriculum and semesters. Show new view.


Filter on which modules contributes to a certain qualification:
-> Show filtering by activity AND architectural layer and group by skill levels

\end{document}
